---
title: "Homework 8"
author: "Donghwan Won"
date: "`r Sys.Date()`"
output: html_document
---
**EID:** dw34446


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(mosaic)

creatinine <- read.csv('C:/Users/namyu/OneDrive/바탕 화면/SDS315/HW8/creatinine.csv')
covid <- read.csv('C:/Users/namyu/OneDrive/바탕 화면/SDS315/HW8/covid.csv')
milk <- read.csv('C:/Users/namyu/OneDrive/바탕 화면/SDS315/HW8/milk.csv')


```


## 1 A
```{r}
creatinine_age = lm(creatclear ~ age, data=creatinine)
coef(creatinine_age)
```
I found the coefficient for creatclear and age. Intercept is 147.81 and age is -0.62. So we have equation for age 55, which is 147.81-(0.62*55)=113.71.

## 1 B
The slope of regression line is -0.62ml/minute per year. This means that creatinine decreases by -0.62ml/minute in every year increases in age.

## 1.C

Creatinine clearance rate for 40 years old is 123.01ml/minute. The equation for this one is 147.81-(0.62*40). They have rate of 135. So residual for 40 years old is 134-123.01= 11.99.

Then creatinine clearance rate for 60 years old is 110.61ml/minute. The equation for this one is 147.81-(0.62*60). They have rate of 120 So residual for 40 years old is 112-110.61
= 1.39.

Since the residual for 40 years old(11.99 ml/minute) is higher than residual for 60 years old(1.39 ml/minute), this indicate that 40 years old people are healthier than 60 years old.

## 2. Italy

```{r}
covid_Italy_subset <- covid[covid$country == 'Italy',]
covid_Italy = lm(log(deaths) ~ (days_since_first_death), data=covid_Italy_subset)
coef(covid_Italy)

boot_Italy = do(10000)*coef(lm(log(deaths) ~ days_since_first_death, data=mosaic::resample(covid_Italy_subset)))
confint(boot_Italy, level = 0.95)


boot_Italy2 = do(10000)*{(70/
coef(lm(log(deaths) ~ days_since_first_death, data=mosaic::resample(covid_Italy_subset))))/100}
confint(boot_Italy2, level = 0.95)


```
I found the coefficient for Italy. Intercept is 1.02 and days_since_first_death is 0.18. Number of deaths grows exponentially at a rate of 1.18 per day in Italy.

After doing bootstrap, we are 95% confident that rate of days_since_first_death is between 0.16 and 0.21. 

After doing bootstrap, we are 95% confident that doubling time for days_since_first_death is between 3.4 days and 4.4 days.

## 2. Spain
```{r}
covid_Spain_subset <- covid[covid$country == 'Spain',]
covid_Spain = lm(log(deaths) ~ (days_since_first_death), data=covid_Spain_subset)
coef(covid_Spain)

boot_Spain = do(10000)*coef(lm(log(deaths) ~ days_since_first_death, data=mosaic::resample(covid_Spain_subset)))
confint(boot_Spain, level = 0.95)

boot_Spain2 = do(10000)*{(70/
  coef(lm(log(deaths) ~ days_since_first_death, data=mosaic::resample(covid_Spain_subset))))/100}
confint(boot_Spain2, level = 0.95)

```
I found the coefficient for Italy. Intercept is 1.02 and days_since_first_death is 0.47. Number of deaths grows exponentially at a rate of 0.28 per day in Spain.

After doing bootstrap, we are 95% confident that rate of days_since_first_death is between 0.23 and 0.32. 

After doing bootstrap, we are 95% confident that doubling time for days_since_first_death is between 2.2 days and 3.0 days.


```{r}
ggplot(covid) + 
  geom_line(aes(x = days_since_first_death, y = deaths, color = country)) +
  labs(
    title = "Daily COVID-19 Deaths in Italy and Spain",
    x = "Days Since First Death",
    y = "Reported Daily Deaths",
    color = "Country"
  )

```

## 3.
```{r}
lm_milk = lm(log(sales) ~ log(price), data=milk)
coef(lm_milk)

boot_milk = do(10000)*coef(lm(log(sales) ~ (price), data=mosaic::resample(milk)))
confint(boot_milk, level = 0.95)

```
Estimated price elasticity of demand for milk is -.55. We are 95% confident that interval of price elasticity is between -0.61 and -0.47. 
For this case, 1% increase in price leads to -0.55% decreases of demand on milk. 
